\vspace{3cm} \Huge{\futhark}\\ \Large{Enhancing performance by rewriting kernels from Python/OpenCL to Futhark}

### 2017-11-08 report/draft.tex
ia

\lstset{
  basicstyle=\tiny,
  showspaces=false,
  showstringspaces=false,
  columns=flexible,
  breaklines=true
}

@@

\section*{Abstract}

@@

\sasmodels has built-in default definitions for $I(q_x,q_y)$ if working
with two-dimensional data, and other functions such as \texttt{form\_volume(q)}
for working with voluminous scatterings.

Therefore, it is optional for the developer to define a custom definition
of $I(q_x, q_y)$ or other default functions.
An example of this can be seen in appendix dab or line.

A minimum viable model is showed in figure \ref{fig:linemodel}, and a more
complex model can be seen in appendix \ref{app:core_shell}

@@

%% figure

@@

\subsubsection{line\_futhark.fut (a Futhark model)}
\label{sec:line-fut}
\begin{figure}
  % hele line_futhark.fut
  \caption{The complete definition of the line model implemented in Futhark.}
  \label{fig:line-fut}
\end{figure}
There a several things happening in this fig. \ref{fig:line-fut}, besides the 
definition of the line Iq function.

@@

\begin{figure}
  % hele for_iq.fut
  % forklar module type
  % forklar module 
  \caption{The Futhark template that is used by the individual models.}
  \label{fig:for-iq}
\end{figure}

@@

\subsection*{DAB model}
\begin{figure}
  \lstinputlisting[language=Python]{../sasmodels/sasmodels/models/dab.py}
  \label{fig:dab}
  \caption{The DAB model}
\end{figure}

\subsection*{broad\_peak model}
\begin{figure}
  \lstinputlisting[language=Python]{../sasmodels/sasmodels/models/broad_peak.py}
  \caption{The broad_peak model}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python]{../sasmodels/sasmodels/models/line.py}
  \caption{The line model}
\end{figure}

\begin{figure}
  \lstinputlisting[]{../sasmodels/sasmodels/models/futharks/line_futhark.fut}
  \label{fig:linemodel-futhark}
  \caption{The line model written in Futhark}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python]{../sasmodels/sasmodels/models/line_futhark.py}
  \caption{The line model info file designating a Futhark path}
\end{figure}

>>>>

\lstset{
  basicstyle=\tiny,
  showspaces=false,
  showstringspaces=false,
  columns=flexible,
  breaklines=true,
  numbers=left
}

@@

\section*{Abstract}
This report describes the design and implementation of a Futhark extension for
the modelling engine \sasmodels.
\sasmodels{} performs small angle scattering calculations for the \sasview{}
modelling suite, by sending it's input to a range of calculation models
implemented in Python and OpenCL.\\\\

%%% whaaaat

@@

\sasmodels{} has built-in default definitions for $I(q_x,q_y)$ if working
with two-dimensional data, and other functions such as \texttt{form\_volume(q)}
for working with voluminous scatterings.

Therefore, it is optional for the developer to define a custom definition
of $I(q_x, q_y)$ or other default functions.
An example of this can be seen in figure \ref{fig:linemodel}.
A more complex model can be seen in appendix \ref{fig:core_shell}

@@

@@

\subsubsection{line\_futhark.fut (a Futhark model)}
\label{sec:line-fut}

\begin{figure}
  \lstinputlisting[]{../sasmodels/sasmodels/models/futharks/line_futhark.fut}
  \caption{The complete definition of the line model implemented in Futhark.}
  \label{fig:linemodel-futhark-full}
\end{figure}

There a several things happening in this fig. \ref{fig:linemodel-futhark-full}, besides the 
definition of the line Iq function.

@@

\begin{figure}
  \lstinputlisting[]{../sasmodels/sasmodels/models/futharks/header/for_iq.fut}
  \caption{The Futhark template that is used by the individual models.}
  \label{fig:for-iq}
\end{figure}

@@

\begin{figure}
  \lstinputlisting[language=Python, firstline=44,lastline=66]{../sasmodels/sasmodels/models/dab.py}
  \label{fig:dabmodel}
  \caption{The DAB model}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python, firstline=44, lastline=94]{../sasmodels/sasmodels/models/broad_peak.py}
  \label{fig:broadpeakmodel}
  \caption{The broad_peak model}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python, linerange={27-55,57-68}]{../sasmodels/sasmodels/models/line.py}
  \label{fig:linemodel}
  \caption{The line model}
\end{figure}

\begin{figure}
  \lstinputlisting[firstline=2, lastline=18]{../sasmodels/sasmodels/models/futharks/line_futhark.fut}
  \label{fig:linemodel-futhark}
  \caption{The line model written in Futhark}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python, firstline=27, lastline=49]{../sasmodels/sasmodels/models/line_futhark.py}
  \label{fig:linemodelinfo-futhark}
  \caption{The line model info file designating a Futhark path}
\end{figure}

\begin{figure}
  \lstinputlisting[language=Python, linerange={131-162}]{../sasmodels/sasmodels/models/core_shell_parallelepiped.py}
  \lstinputlisting[language=C, linerange={10-81}]{../sasmodels/sasmodels/models/core_shell_parallelepiped.c}
  \label{fig:core_shell}
  \caption{The original core\_shell\_parallelepiped model (Iq and form volume)}
\end{figure}
